---
title: "Fisher's exact test"
author: "AJ"
date: "27/02/2022"
output: html_notebook
---
# Performing fisher's exact test
This script is to perform fisher's exact test to test association between habitat type, seasonality and time of the day with sighting of P cantorii. 

```{r}
library(rcompanion)
library(Matrix)
```

## fisher's exact test for association between Habitat type and sighting

```{r}
Input =("
Frequency Seen Not_Seen
Isolated_Pool 31 46
Flowing_river 33 44
        ")
Matriz = as.matrix(read.table(textConnection(Input),
                              header=TRUE,
                              row.names=1))
Matriz
fisher.test(Matriz, alternative="two.sided")
```
## fisher's exact test for association between seasonality and sighting
```{r}
Input =("
Frequency Seen Not_Seen
Dry_season 40 33
Monsoon 7 66
        ")
Matriz_2 = as.matrix(read.table(textConnection(Input),
                              header=TRUE,
                              row.names=1))
Matriz_2
fisher.test(Matriz_2,
            alternative="two.sided")



```
## fisher's exact test for association between time of the day and sighting
```{r}
Input =("
Frequency Seen Not_Seen
Day 70 64
Night 18 116
        ")
Matriz_3 = as.matrix(read.table(textConnection(Input),
                              header=TRUE,
                              row.names=1))
Matriz_3
fisher.test(Matriz_3,
            alternative="two.sided")


```

